No Replication Without Process Documentation:  An Assessment of Management

### 2020-03-26 R/MSE manuscript.Rmd
Edit through objectives

Are the results of MSE living up to their descriptions? Are MSEs evaluating trade-offs and the consequences of uncertainty? Do they test potential harvest strategies? Were the management objectives used to evaluate management proceedures established and agreed to? Was a 'best' management strategy identified? Was consideration given to the weights on objectives, preferences, and attitudes to risk?

@@

ARe MSE processes being conducted in the manner described? Do MSE processes consider and account for the interface between science and policy? Are scientists, managers and stakeholders involved and communicating through and iterative process that creates buy-in?

>>>>

Are the results of MSE living up to their descriptions? Are MSEs evaluating trade-offs and the consequences of uncertainty? Do they test potential harvest strategies? Were the management objectives used to evaluate management procedures established and agreed to? Was a 'best' management strategy identified? Was consideration given to the weights on objectives, preferences, and attitudes to risk?

@@

Are MSE processes being conducted in the manner described? Do MSE processes consider and account for the interface between science and policy? Are scientists, managers and stakeholders involved and communicating through and iterative process that creates buy-in?
